Real-time resolution of short-read assembly graph using ONT long reads

### 2020-11-23 paper_clean.tex
done

\nolinenumbers
\pagebreak
\section*{List of figures}

@@

>>>>

\nolinenumbers
\pagebreak
\section*{List of legends}

@@

\paragraph*{Fig S1}
Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}. Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs. On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.

\paragraph*{Fig S2}
Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.

\paragraph*{Table S1}
Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.

### 2020-11-23 paper_edit.tex
done

\nolinenumbers
\pagebreak
\section*{List of figures}

@@

>>>>

\nolinenumbers
\pagebreak
\section*{List of \review{legends}}

@@

\review{
\paragraph*{Fig S1}
Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}. Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs. On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.
}

\review{
\paragraph*{Fig S2}
Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.
}

\review{
\paragraph*{Table S1}
Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.
}
